---
title: "CHPD Daily Replication"
output:
  word_document:
  html_document:
    df_print: paged
always_allow_html: yes
---

Useful source for understanding RMarkdown: https://bookdown.org/yihui/markdown-cookbook

To knit the daily without any code chunks, you can set the parameters in code chunks options. Note that figure captions is a parameter in the code chunk. The full list of code chunk options can be found here: https://yihui.org/knitr/options/

Use `echo=FALSE` when coding to see the outputs in the RMarkdown. Once everything is ready to be knit, change it to `include=FALSE`.

```{r, include=FALSE, warning=FALSE}
# Import packages
library(tidyverse)
library(data.table)
library(janitor)
library(plotly)

# Source the functions
source("daily_functions.R")
```

```{r, include=FALSE}
# Load the data

# Read the csv file and clean the column names
df <- clean_names(read.csv("./Data/13100111.csv"))

# Display the data frame. When knit, the entire data frame is shown column by column which creates many pages, so let's use the head() function to check it was read.
head(df)

# Print the column names. This will make it easier to select which columns to keep
print(colnames(df))
```

```{r, include=FALSE}
# Data manipulation

# Select which columns to keep
df <- select(df, c("i_ref_date", "geo", "age_group", "sex", "primary_types_of_cancer_icd_o_3", 
                   "characteristics", "value", "uom"))

# Clean the primary type of cancer column
# Remove anything after the cancer type
df$primary_types_of_cancer_icd_o_3 <- gsub(" \\[[^\\]]*\\]", "", df$primary_types_of_cancer_icd_o_3, perl = TRUE)

# Display
head(df)
```

```{r, include=FALSE}
# Find NAs in value
sapply(df, FUN = function(x) sum(is.na(x)))

df <- df[!is.na(df$value), ]
```

```{r, include=FALSE}
# Find the most commonly diagnosed cancer

# Get the unique list of cancers
unique(df$primary_types_of_cancer_icd_o_3)

# Find the most commmon cancer type in Canada for all ages, both sexes per year
mostCommon <- df %>%
  
  # Filter (Note: From 2011 to 2017, Quebec was excluded)
  filter(geo %in% c("Canada", "Canada (excluding Quebec)"),
         age_group == "Total, all ages",
         sex == "Both sexes",
         primary_types_of_cancer_icd_o_3 != "Total, all primary sites of cancer",
         characteristics == "Number of new cancer cases") %>%
  
  # Group by reference period
  group_by(i_ref_date) %>%
  
  # Filter for the max
  filter(value == max(value)) %>%
  
  # Display from most recent to least recent
  arrange(desc(i_ref_date))

mostCommon
```

```{r, include=FALSE}
# Save the mode for the most common type of cancer
mcCancer <- get_mode(mostCommon$primary_types_of_cancer_icd_o_3)

mcCancer
```

Assume that the daily will be written for the current year.

# Canadian Cancer Statistics: A `r format(Sys.Date(), "%Y")` special report on `r mcCancer` Cancer

## `r mcCancer` cancer most commonly diagnosed cancer and leading cause of cancer death
```{r, echo = FALSE, results='asis'}
# Note 1: Did not do the analysis for sum of colorectal, pancreatic, and breast cancers or the statistic for 2020 and estimated death toll.
# Note 2: Formatting such as italics, bolding, underlining, etc. will have to be done in Word.


p <- str_glue(

"{mcCancer} cancer is the most commonly diagnosed cancer and the leading cause of cancer death in Canada. More Canadians die of {mcCancer} cancer than colorectal, pancreatic and breast cancers combined. In {format(Sys.Date(), \"%Y\")} alone, it is estimated that more than 21,000 Canadians are expected to die of {str_to_lower(mcCancer)} cancer. The high rate of death (mortality rate) from {str_to_lower(mcCancer)} cancer reflects both its high rate of diagnosis (incidence rate) and its low survival.

The Canadian Cancer Statistics: A {format(Sys.Date(), \"%Y\")} special report on {mcCancer} cancer, developed by the Canadian Cancer Statistics Advisory Committee in collaboration with the Canadian Cancer Society, Statistics Canada and the Public Health Agency of Canada, provides new insight into {str_to_lower(mcCancer)} cancer patterns in Canada. The report also provides information on important and emerging issues related to {str_to_lower(mcCancer)} cancer, such as risk factors, screening and treatment. While the results predate the COVID–19 pandemic, they provide a baseline with which to eventually gauge the impact of the pandemic on rates of {str_to_lower(mcCancer)} cancer incidence, mortality and survival.
"
)

p
```

```{r, include=FALSE}
# Check the unique values in these columns
unique(df$age_group)
unique(df$sex)
unique(df$characteristics)
```

```{r, include=FALSE}
# Finding trends with incidence rates

# Take note of the uom.
uom <- "Rate per 100,000 population"

irAgeSex <- df %>%
  
  # Filter the data. Note: if wanted most recent year(s), would add it as a filter
  filter(geo %in% c("Canada", "Canada (excluding Quebec)"),
         age_group != "Total, all ages",
         age_group != "Age group, not stated",
         sex != "Both sexes",
         primary_types_of_cancer_icd_o_3 == "Lung and bronchus",
         characteristics == "Cancer incidence rate") %>%
  
  # Select which columns to keep (Know that it's lung and bronchus cancer and cancer incidence rate)
  select(., c("i_ref_date", "geo", "age_group", "sex", "value"))

irAgeSex
```

```{r, include=FALSE}
irAgeSex2017 <- df%>%
  
  # Filter the data. Note: if wanted most recent year(s), would add it as a filter
  filter(i_ref_date == 2017,
         geo %in% c("Canada", "Canada (excluding Quebec)"),
         age_group != "Total, all ages",
         age_group != "Age group, not stated",
         sex == "Both sexes",
         primary_types_of_cancer_icd_o_3 == "Lung and bronchus",
         characteristics == "Cancer incidence rate") %>%
  
  # Select which columns to keep (Know that it's lung and bronchus cancer and cancer incidence rate)
  select(., c("i_ref_date", "geo", "age_group", "sex", "value"))


irAgeSex2017
```

```{r, include=FALSE}
# Calculate the age group by age group difference
irAgeSex2017 <- irAgeSex2017 %>%
  mutate(val_change = value-lag(value))

# Replace the NA value in the first row
irAgeSex2017$val_change[is.na(irAgeSex2017$val_change)] <- 0

# Gives sign to indicate if there was an increase or decrease
irAgeSex2017$Sign <- sign(irAgeSex2017$val_change)

irAgeSex2017
```

```{r, include=FALSE}
# Check if there was a large change
# Input: x - A list; thr - the threshold to determine "large" (numeric)
# Ouput: dramatically or the null character

# Feature: Have a list of synonyms for dramatically, and randomly return one if true

isDramatic <- function(x, thr){
  
  # Take the absolute value for each item in the list 
  a <- abs(x)
  
  # If the absolute range is large, the change was drastic
  if(max(a)-min(a) > thr) {
    
    return("dramatically")
    
  } else {
    
    return("")
    
  }
  
}

# Check if there was an overall change and indicate its direction. First value - last value. Assumes the data frame is sorted by one of its columns
# Input: x - A list
# Ouput: dramatically or the null character

isChange <- function(x) {
  
  # If the first value is less than the last value, there was an increase
  if(head(x, 1) < tail(x, 1)) {
    
    return("increase")
    
  # Else if the first value is larger than the last value, there was a decrease
  } else if (head(x, 1) > tail(x, 1)) {
    
    return("decrease")
    
  # Else there was no change
  } else {
    
    return("do not change")
    
  }
}
```

```{r, include=FALSE}
ag <- irAgeSex2017 %>%
  filter(value == max(value))

ag$age_group
```

```{r, include=FALSE}
# Compare incidence rate between sexes
irAgeSex <- df %>%
  
  # Filter the data.
  filter(i_ref_date == "2017",
         geo %in% c("Canada", "Canada (excluding Quebec)"),
         age_group != "Total, all ages",
         age_group != "Age group, not stated",
         sex != "Both sexes",
         primary_types_of_cancer_icd_o_3 == "Lung and bronchus",
         characteristics == "Cancer incidence rate") %>%
  
  # Select which columns to keep (Know that it's lung and bronchus cancer and cancer incidence rate)
  select(., c("i_ref_date", "geo", "age_group", "sex", "value"))

irAgeSex

irAgeSexAvg <- irAgeSex %>%
  
  group_by(sex) %>%
  
  summarise(average = mean(value))
  
  #mutate(val_change = value-lag(value))

# Replace the NA value in the first row
#irAgeSex$val_change[is.na(irAgeSex$val_change)] <- 0

# Will always return sex in alphabetical order
irAgeSexAvg

gir <- gr(irAgeSexAvg$average[1], irAgeSexAvg$average[2], "females", "males")

pct_dif(irAgeSexAvg$average[2], irAgeSexAvg$average[1])
```

```{r, include=FALSE}
irAgeSex17 <- irAgeSex %>%
  
  # Group_by age group
  group_by(age_group) %>%
  
  # Find the difference between females and males (females are always second)
  summarise(fm_diff = value[2]-value[1])

# Reorder 5 to 9 years to be the 2nd row
irAgeSex17 <- irAgeSex17[c(1, 10, 2:9, 11:19), ]

irAgeSex17
```


# `r mcCancer` cancer rates `r isChange(irAgeSex2017$value)` `r isDramatic(irAgeSex2017$value, 300)` with age and are higher among `r gir[1]` than `r gir[2]`
```{r, echo = FALSE, results='asis'}
# Note: The data did not have mortality data, but it would follow the same steps as incidence rate
# For the last sentence, it is easier to look at the fm_diff table to identify the trend than to automate it. If automation is necessary, have an analyst determine what the best approach for this is.

p2 <- str_glue("{mcCancer} cancer incidence and mortality rates {isChange(irAgeSex2017$value)} {isDramatic(irAgeSex2017$value, 300)} with age. Incidence rates peak among Canadians aged {ag$age_group} ({unitMeasure(uom, floor(ag$value), \"people\")}), while mortality rates peak among Canadians aged 85 years and older ({unitMeasure(uom, 352, \"people\")}). Overall, the incidence rate of {str_to_lower(mcCancer)} cancer is about {round(pct_dif(irAgeSexAvg$average[2], irAgeSexAvg$average[1]))}% higher among {gir[1]} than {gir[2]} and the mortality rate is about 31% higher among males than females. However, among Canadians younger than 55 years of age, rates are higher among females than males.
"
)

p2
```

```{r, include=FALSE}
irAgeSex92v12 <- df %>%
  
  # Filter the data.
  filter(i_ref_date %in% c("1992", "2012"),
         geo %in% c("Canada", "Canada (excluding Quebec)"),
         age_group == "Total, all ages",
         sex != "Both sexes",
         primary_types_of_cancer_icd_o_3 == "Lung and bronchus",
         characteristics == "Cancer incidence rate") %>%
  
  # Select which columns to keep (Know that it's lung and bronchus cancer and cancer incidence rate)
  select(., c("i_ref_date", "geo", "age_group", "sex", "value"))

irAgeSex92v12
```

```{r, include=FALSE}
irAgeSex92v12 <- df %>%
  
  # Filter the data.
  filter(i_ref_date %in% c(1992, 2012),
         geo %in% c("Canada", "Canada (excluding Quebec)"),
         age_group == "Total, all ages",
         sex != "Both sexes",
         primary_types_of_cancer_icd_o_3 == "Lung and bronchus",
         characteristics == "Cancer incidence rate") %>%
  
  # Select which columns to keep (Know that it's lung and bronchus cancer and cancer incidence rate)
  select(., c("i_ref_date", "geo", "age_group", "sex", "value"))

irSex_diff <- df %>%
  
  # Filter the data.
  filter(i_ref_date %in% c(1992:2012),
         geo == "Canada (excluding Quebec)",
         age_group == "Total, all ages",
         sex != "Both sexes",
         primary_types_of_cancer_icd_o_3 == "Lung and bronchus",
         characteristics == "Cancer incidence rate") %>%
  
  # Select which columns to keep (Know that it's lung and bronchus cancer and cancer incidence rate)
  select(., c("i_ref_date", "geo", "sex", "value"))  %>%
  
  # Group_by age group
  group_by(sex) %>%
  
  # Find the difference between years for females and males
  summarise(fm_diff = value[2]-value[1], .groups = "drop")

# Display
irSex_diff

# Filter by respective sex
irMale_diff <- filter(irSex_diff, sex == "Males")
irFemale_diff <- filter(irSex_diff, sex == "Females")

# Filter for recent years
irSexRecent_diff <- df %>%
  
  # Filter the data.
  filter(i_ref_date %in% c(2013:2017),
         geo == "Canada (excluding Quebec)",
         age_group == "Total, all ages",
         sex != "Both sexes",
         primary_types_of_cancer_icd_o_3 == "Lung and bronchus",
         characteristics == "Cancer incidence rate") %>%
  
  # Select which columns to keep (Know that it's lung and bronchus cancer and cancer incidence rate)
  select(., c("i_ref_date", "geo", "sex", "value"))  %>%
  
  # Group_by age group
  group_by(sex) %>%
  
  # Find the difference between years for females and males
  summarise(fm_diff = value[2]-value[1], .groups = "drop")

# Display
irSexRecent_diff

# Filter for respective sex
irMaleRecent_diff <- filter(irSex_diff, sex == "Males")
irFemaleRecent_diff <- filter(irSex_diff, sex == "Females")

# Compare rates between female and male
rate <- case_when(irMaleRecent_diff$fm_diff < 0 & irFemaleRecent_diff$fm_diff < 0 ~ "decreasing in both sexes",
                  irMaleRecent_diff$fm_diff > 0 & irFemaleRecent_diff$fm_diff < 0 ~ "increasing in males and decreasing in females",
                  irMaleRecent_diff$fm_diff < 0 & irFemaleRecent_diff$fm_diff > 0 ~ "increasing in females and decreasing in males",
                  irMaleRecent_diff$fm_diff > 0 & irFemaleRecent_diff$fm_diff > 0 ~ "increasing in both sexes"
                  )
```

# Rates of diagnosis of `r str_to_lower(mcCancer)` converging over time between males and females
```{r, echo = FALSE, results='asis'}
# For the last couple of sentences, it is easier to look at the fm_diff table to identify the trend than to automate it. If automation is necessary, have an analyst determine what the best approach for this is.

p3 <- str_glue("While {str_to_lower(mcCancer)} cancer incidence rates are higher among males than females, these rates have been getting closer over time. In 1992, the {str_to_lower(mcCancer)} cancer incidence rate among males ({unitMeasure(uom, irAgeSex92v12$value[3], \"males\")}) was almost over twice that recorded among females ({unitMeasure(uom, irAgeSex92v12$value[4], \"females\")}). However, by 2012 the gap had narrowed considerably ({unitMeasure(uom, irAgeSex92v12$value[5], \"males\")} versus {unitMeasure(uom, irAgeSex92v12$value[6], \"females\")}) due to {case_when(irMale_diff$fm_diff < 0 ~ \"decreasing\", irMale_diff$fm_diff > 0 ~ \"increasing\", TRUE ~ \"constant\")} rates among males and {case_when(irFemale_diff$fm_diff < 0 ~ \"decreasing\", irFemale_diff$fm_diff > 0 ~ \"increasing\", TRUE ~ \"constant\")} rates among females. Rates have subsequently been {rate}, but more quickly among males.
               
The difference in {str_to_lower(mcCancer)} cancer rates in males and females over time largely reflects past differences in tobacco smoking. Among males, a decrease in the prevalence of daily smoking began in the mid-1960s, preceding the decrease in {str_to_lower(mcCancer)} cancer incidence by about 20 years. Among females, the decrease in daily smoking did not start until the 1980s. Trends in {str_to_lower(mcCancer)} cancer mortality rates largely follow trends in {str_to_lower(mcCancer)} cancer incidence.")

p3
```

```{r, include=FALSE}
# Load the data
lineGraph <- read.csv("./Data/lg_data.csv", strip.white = TRUE, na.strings = NA, skip = 1)

# Rename the first column to Year
names(lineGraph)[1] <- c("Year")

# Store the last row value
source <- tail(lineGraph$Year, 1)

source <-paste(source)

# Remove it
lineGraph <- head(lineGraph, -1)

# Convert factor type to numeric
#lineGraph$Year <- as.numeric(levels(lineGraph$Year)[lineGraph$Year])
lineGraph$Year <- as.numeric(lineGraph$Year)

# Display
lineGraph
```

```{r, include=FALSE}
# Unfortunately, Plotly graphs cannot be knit to word. However, they can be knit to html and then saved. You will then have 2 options to insert the image into word. 1. Insert Image in Word as you would do any image. 2. Have RMarkdown knit the image to word using this command: `![Caption][Path/to/plot.png]`

# Plot the data
lg <- plot_ly(lineGraph, x = ~Year, y = ~Male, name = "Male", type = 'scatter', mode = 'lines') %>%
  add_trace(y = ~Female, name = "Female", mode = 'lines') %>%
  layout(title = list(text = "Rate (per 100,000 people)", x = 0.01),
         xaxis = list(title = "", dtick = 2),
         yaxis = list(title=""),
         legend = list(orientation = 'h'),
         annotations = list(x = -0.08, y = -0.2, text = source, showarrow = FALSE, xref="paper", yref="paper"))

lg
```

# Chart 1
# Age-standardized incidence rate trend of lung cancer, by sex, Canada excluding Quebec, 1992 to 2016
```{r, echo=FALSE, fig.cap="Source(s): Canadian Cancer Registry (3207)."}
# Pivot data for ggplot
lineGraph <- pivot_longer(lineGraph, cols = c("Male", "Female"), names_to = "Sex", values_to = "Rate")

# Define order of legend
lineGraph$Sex <- factor(lineGraph$Sex, levels = c("Male", "Female"))

lg <- ggplot(lineGraph, aes(x=Year, y=Rate, group=Sex)) +
  geom_line(aes(color=Sex)) +
  labs(title = "Rate (per 100,000 people)", x = "", y = "") +
  scale_x_continuous(breaks=seq(1992, 2016, 2)) +
  theme_linedraw() + 
  theme(legend.position = "bottom", 
        legend.title = element_blank(),
        panel.grid = element_blank())

lg
```

# `r mcCancer` cancer survival higher among females than males
```{r, echo = FALSE, results='asis'}
# Note: For p4 and p5, I did not have the data to generate their values

p4 <- str_glue("{mcCancer} cancer survival is typically higher among females than males, regardless of age or province at diagnosis. For example, five-year net survival among females was 22%, compared with 15% among males. While survival tends to be higher among females for many cancers, the strength of this advantage among str_to_lower(mcCancer) cancer patients is particularly notable.")

p4
```

# About half of `r str_to_lower(mcCancer)` cancer cases are diagnosed at the latest stage when survival is extremely low
```{r, echo = FALSE, results='asis'}
p5 <- str_glue("Staging is a way of classifying a cancer based on the extent of disease in the body at the time of diagnosis. Staging levels typically run from I to IV, with the higher number indicating greater spread of disease in the body from the origin of the cancer. About half of all str_to_lower(mcCancer) cancers are diagnosed at stage IV, at which point survival is extremely low—three-year net survival of 5%. In contrast, slightly less than 1 in 10 str_to_lower(mcCancer) cancers are diagnosed at stage I where the cancer is relatively small and contained within the lung and the three-year prognosis is much better (71%).")

p5
```

# Chart 2
# Lung cancer three-year predicted net survival estimates by stage at diagnosis, Canada excluding Quebec, 2012–2014
```{r, include=FALSE}
# Load the data
barGraph <- read.csv("./Data/bar_data.csv", header = FALSE, strip.white = TRUE, na.strings = NA, skip = 1)

# Rename the first column to Year
names(barGraph) <- c("Stage", "Net Survival (%)")

# Store the last row value
source <- tail(barGraph$Stage, 1)

# Make the annotation 1 string
source <- str_squish(paste(source))

source

# Remove last row
barGraph <- head(barGraph, -1)

# Convert factor type to numeric
#barGraph$Stage <- as.character(levels(barGraph$Stage)[barGraph$Stage])

# Display
barGraph
```

```{r, include=FALSE}
# Plot the data
bg <- plot_ly(map_df(barGraph, rev), x = ~`Net Survival (%)`, y = ~Stage, type = 'bar', orientation = 'h') %>%
  layout(xaxis = list(title = "Net Survival (%)", dtick = 20),
         # Specify the order of the columns, for some reason the data frame had to be reversed as well
         yaxis = list(title = "", categoryorder="array", categoryarray = ~Stage),
         margin = list(b = 100, pad = 20),
         # Instead of using an annotation, I would recommend just printing the caption underneath the graph as done 
         # in the daily or you can add the fig.cap parameter at the top of the chunk and type/paste the caption.
         annotations = list(x = -0.2, y = -0.25, text = source, font=list(size=7.8), 
                            showarrow = FALSE, xref="paper", yref="paper"))

bg
```

```{r, echo=FALSE, fig.cap="Source(s): Canadian Cancer Registry (3207) linked to mortality data from the Canadian Vital Stats Death Database (3233) and death information from the T1 Personal Master File (CCR-CVSD-T1PMF)."}

# Specify the order
barGraph$Stage <- factor(barGraph$Stage, levels=(rev(barGraph$Stage)))

bg <- ggplot(barGraph, aes(x = Stage, y = `Net Survival (%)`)) +
  geom_col(fill="skyblue2", color="black") +
  scale_y_continuous(breaks = seq(0, 80, 20), expand = expansion(mult=c(0,0.1))) +
  labs(x = "") +
  theme_linedraw() + 
  theme(panel.grid = element_blank()) +
  coord_flip()

bg
```

